Exploring the Shadows of Terror: The Influence of Terrorism on Public Opinion and Democratic Values

### 2024-02-14 outputs/paper/paper.qmd
scriptes for simulate, download, test

## Source
Our study is based on a detailed examination by Amélie Godefroidt published in 2022 in the American Journal of Political Science. This important research looks into how terrorism affects what people think about democracy and politics, using a wide range of examples from small local attacks to large international ones. We aim to do more research based on Godefroidt's work, using her collection of data from 241 papers, which cover 326 studies and provide 1,733 measurements of how terrorism influences people's political views. This collection of information, gathered through careful research and organization, is the main resource for our study as we explore the complex effects of terrorism in different settings around the world.

@@

```{r }
#| label: fig-terrorism-trend
#| fig-cap: Summary of Data Included in theMeta-Analysis
#| echo: false
#| warning: false
#| message: false
#| out.width: "90%"  # Adjust to fit the page
#| out.height: "90%"  # Adjust to fit the page

@@

```{r}
#| label: fig-reactions-to-terrorism
#| fig-cap: Relationship between Terrorism and Political Attitudes Conditional on Substantive and Methodological Factors
#| echo: false
#| warning: false
#| message: false
#| out.width: "90%"  # Adjust to fit the page
#| out.height: "90%"  # Adjust to fit the page
knitr::include_graphics("../../outputs/figures/Figure2.jpeg")
```

>>>>

## Source
Our study is based on a detailed examination by Amélie Godefroidt published in 2022 in the American Journal of Political Science. This important research looks into how terrorism affects what people think about democracy and politics, using a wide range of examples from small local attacks to large international ones. We aim to do more research based on Godefroidt's work [@AmelieData], using her collection of data from 241 papers, which cover 326 studies and provide 1,733 measurements of how terrorism influences people's political views. This collection of information, gathered through careful research and organization, is the main resource for our study as we explore the complex effects of terrorism in different settings around the world.

@@

```{r }
#| label: fig-terrorism-trend
#| fig-cap: Summary of Data Included in the Meta-Analysis [@AmelieData]
#| echo: false
#| warning: false
#| message: false
#| out.width: "90%"  # Adjust to fit the page
#| out.height: "90%"  # Adjust to fit the page

@@

```{r}
#| label: fig-reactions-to-terrorism
#| fig-cap: Relationship between Terrorism and Political Attitudes Conditional on Substantive and Methodological Factors [@AmelieData]
#| echo: false
#| warning: false
#| message: false
#| out.width: "90%"  # Adjust to fit the page
#| out.height: "90%"  # Adjust to fit the page
knitr::include_graphics("../../outputs/figures/Figure2.jpeg")
```
